---
title: "Introduction to Biomedical Data Science / Homework-2"
author:
date:
output:
    html_document:
        toc: true
        toc_depth: 2
        number_sections: true
---


# Play with some pre-made data

## Load

- Read `data/data1.rds`
- Read `data/data2.rda`
- Read `data/data3.rdata`

```{r}

data1 <- readRDS("data/data1.rds")

load("data/data2.rda")

load("data/data3.rdata")

```

## Examine

- Show the type of each data object
- Show the length of `data2`
- Show the first item of `data1`
- Write a logic comparison testing whether the fourth item of `data2` is a "k"
- What is the largest number in `data1`
    - You can use `sort` and numerical indexing to get the answer
    - Or, is there a function for this already? Ask Google
- Calculate the summary of `data3` and assign it to the variable `data3_sum`
- Show the ratio of "female" to "male" in `data3_sum`
- Subtract 10 from each element of `data1` and calculate the new average (no need to create new variable)

```{r}

class(data1)
class(data2)
class(data3)

length(data2)

data1[1]

data2[4] == "k"

# Find largest in data1
tail(sort(data1))
max(data1)

data3_sum <- summary(data3)

data3_sum["female"] / data3_sum["male"]

mean(data1-10)


```


## Manipulate and save

- Make a vector named `new_vec` using all the numbers in `data1` larger than 50
- Shorten `data2` by selecting the first 100 items and store it with a new name `data2_short`
- Append string `"AAA"` to each element of `data2_short` and save this as a new object `data2_appended` (hint: use `paste()` function with empty string "" as separator)
- Save `data2_short` in data folder as an `.rds` file
- Save `data2_appended` in data folder as a `.rda` file


```{r}

new_vec <- data1[data1 > 50]

data2_short <- data2[1:100]

data2_appended <- paste("AAA", data2_short, sep = "")

saveRDS(data2_short, "data/data2_short.rds")

save(data2_appended, file = "data/data2_appended.rda" )

```


# Create an unfair die function

- The die has 6 faces like normal but number 6 is twice likelier to turn up. (Hint: think of it as having 7 faces but with two 6's)
- Write a function that rolls the dice for a user-defined number of times and outputs a vector of the result.
- Save this function as an Rscript under `scripts` folder
- Source the script into Rmarkdown chunk below
- `set.seed` to `222`, roll the dice 200 times, and store the results in `result` object
- What is the position of the first occurrence of 3 (Hint: use `which` function and `==`)
- How many times did the die roll 6? (Hint: use `==` and add all the instances of die being 6)
- How many times did each face turned up (Hint: use `summary` after converting result to `factor`)

```{r}

source("scripts/unfair_die.R")

set.seed(222)

result <- unfair_die()

which(result == 3)

sum(result == 6)

summary(factor(result))

```


# BONUS QUESTION: Learn and use new functions yourself

- You will use `list()`, `lapply()`, and `dim()` functions
- Create a list named `my_list` that contains three elements
- These elements should be R built-in data frames: `cars`, `pressure`, `airquality`
- Use `lapply()` function on the list to report dimensions (`dim`) of each data frame


```{r}

my_list <- list(cars, pressure, airquality)

lapply(my_list, dim)

```





